Untitled

### 2023-10-13 code/analysis_Redo.Rmd
friday commit
Cleaning up the code for final analysis

```{r}
dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 40, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

uds.sites.full %>%
  filter(is.na(Zip))
```

@@

@@

## Broken down by components
```{r}

df.core <- dfc %>% 
  mutate( MCD = Total * Pct.MCD / 100,
         None = Total * Pct.None / 100,
         MCR = Total * Pct.MCR / 100,
         COM = Total * Pct.COM / 100,

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         MCD:COM, 
         crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

for (j in 10:23){

  df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )

  did.core <- rbind(did.core, outcomes$coeftable)

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(MCD:NetWorth) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = MCD:NetWorth) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

## Panel Complexity and Intensity of Care
```{r}

@@

@@

df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50) %>%

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  #mutate(Sites = log(Sites + 1)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

@@

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    TEs <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "SL", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
  }

    TEs

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Farthest 20% of Zips")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Competitive Zip")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Farthest 20% of Zips")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Competitive Zip")

@@

event_study(data = df.rival, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")

>>>>

```{r}
mean.nas<- function(x){ mean(x, na.rm = TRUE)}

options(scipen=999)
```

```{r}
dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

uds.sites.full %>%
  filter(is.na(Zip))

@@

summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Total ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
```

## Broken down by components
```{r}
# 
# df.core <- dfc %>% 
#   mutate( MCD = Total * Pct.MCD / 100,
#          None = Total * Pct.None / 100,
#          MCR = Total * Pct.MCR / 100,
#          COM = Total * Pct.COM / 100,
#          
#          crc.rate = crc.rate * 100, 
#          pap.rate = pap.rate * 100, 
#          childbmi.rate = childbmi.rate * 100, 
#          adultbmi.rate = adultbmi.rate * 100, 
#          htn.rate = htn.rate * 100, 
#          dm.rate = dm.rate * 100) %>% 
#   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
#          MCD:COM, 
#          crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
#          Liquidity:NetWorth, 
#          Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman) 
#   
# 
# 
# 
# did.core <- c(0, 0, 0, 0)
# 
# for (j in 10:23){
#   
#   df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
#   colnames(df.temp)[10] <- "Outcome"
#   outcomes <- did2s(
#       data = df.temp, 
#       yname = "Outcome", 
#       treatment = "Tx",
#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
#         second_stage = ~ i(Tx, ref = FALSE),
#         cluster_var = "STATE",
#       verbose = FALSE
#     )
#   
#   did.core <- rbind(did.core, outcomes$coeftable)
#   
#   
# }
# 
# 
# did.core <- did.core[-1,]
# rownames(did.core) <- NULL
#

# 
# df.core %>% 
#   mutate(Post = ifelse(year.rel >= 0, 1, 0), 
#          Treated = ifelse(Att > 0, 1, 0)) %>% 
#   group_by(Post, Treated) %>% 
#   select(MCD:NetWorth) %>% 
#   summarise_all(mean.nas) %>% 
#   # summarise(Total = mean(Total, na.rm = TRUE), 
#   #           Quality = mean(Qcomp, na.rm = TRUE), 
#   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
#   pivot_longer(cols = MCD:NetWorth) %>% 
#   mutate(value = round(value, 2)) %>% 
#   #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
#   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
#   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
#   cbind(did.core) %>% 
#    select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
#   mutate(Estimate = round(Estimate, 2), 
#          `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
#          `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
#   rename(Outcome = name) %>% 
#   select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
#   kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
#   kable_styling(latex_options = c("striped")) %>%
#   pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
#   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
# 
#

@@

## Patient Selection on Panel Complexity and Intensity of Care
```{r}

@@

summary(lm(data = df.select.stint %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Complexity ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.select.stint %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Intensity ~ Treated*year.rel))$coeff[4,]

## Patient Selection on Payer Mix
```{r}

df.select.payer <- dfc %>% 
  mutate( MCD = Total * Pct.MCD / 100,
         None = Total * Pct.None / 100,
         MCR = Total * Pct.MCR / 100,
         COM = Total * Pct.COM / 100,

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

did.select.payer <- c(0, 0, 0, 0)

for (j in 10:17){

  df.temp <- df.select.payer[,c(1:9, j, 18:ncol(df.select.payer))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = FALSE
    )

  did.select.payer <- rbind(did.select.payer, outcomes$coeftable)

did.select.payer <- did.select.payer[-1,]
rownames(did.select.payer) <- NULL

df.select.payer %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(MCD:Pct.COM) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = MCD:Pct.COM) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.select.payer) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Total Patients by Payer" = 4, "Payer Mix, %" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

pm1 <- event_study(data = df.select.payer, 
  yname = "MCD", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

pm2 <- event_study(data = df.select.payer, 
  yname = "COM", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

pm3 <- event_study(data = df.select.payer, 
  yname = "MCR", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

pm4 <- event_study(data = df.select.payer, 
  yname = "None", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

pm <- ggarrange(pm1, pm2, pm3, pm4, common.legend = TRUE)
pm

summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), MCD ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), None ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), MCR ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), COM ~ Treated*year.rel))$coeff[4,]

@@

df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50 ) %>% 
  #group_by(Zip) %>% mutate(MaxNum = max(NumberofPatients)) %>% filter(MaxNum > 50) %>%

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  #mutate(Sites = log(Sites + 1)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)

#%>% filter(Zip != '04401')
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

@@

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

    tes

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

@@

rpm1 <- event_study(data = df.rival, 
  yname = "MCD", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

rpm2 <- event_study(data = df.rival, 
  yname = "COM", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")

rpm3 <- event_study(data = df.rival, 
  yname = "MCR", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
